% ── 2.1 Data Source Evaluation ───────────────────────────────────────────────
\subsection{Data Source Evaluation}
\label{sec:data_sources}

Polymarket operates on the Polygon blockchain, a proof-of-stake Ethereum
sidechain chosen for its low transaction fees and high throughput.
Every trade settles on-chain via the \textit{CTF Exchange} smart contract,
which implements Gnosis's Conditional Token Framework (CTF)~\cite{polymarket_ctf}.
When a market is created, USDC collateral is used to mint a complementary
pair of ERC-1155 outcome tokens — one \texttt{YES} and one \texttt{NO} —
each redeemable for \$1\,USDC if its outcome resolves true, and worthless
otherwise.
Order matching is hybrid-decentralised: a central limit order book (CLOB)
matches orders off-chain, but all fills are submitted to and permanently
recorded by the on-chain exchange contract as \texttt{OrderFilled}
events~\cite{polymarket_docs}.
This architecture means the full trade history — including the wallet
addresses of both the maker and taker in every fill — is publicly
queryable from the blockchain.

Accessing that history at scale required evaluating several data sources.
Table~\ref{tab:data_sources} summarises the three most viable options
considered.
Several further blockchain data platforms were evaluated and rejected
outright for coverage or access reasons: the Polymarket CLOB API
\texttt{/trades} endpoint is user-scoped and returns empty results for
market-level queries; Allium (\texttt{predictions.allium.so}) requires
enterprise approval and is not publicly accessible; CryptoHouse
(\texttt{crypto.clickhouse.com}) carries no Polymarket data at all;
and the Goldsky \texttt{polymarket-orderbook-resync/prod} subgraph,
while current, omits maker and taker wallet addresses entirely —
making it unsuitable for any wallet-level analysis.

\begin{table}[H]
\centering
\caption{Primary data sources evaluated for trade history acquisition.}
\label{tab:data_sources}
\small
\begin{tabularx}{\textwidth}{p{3.8cm} p{3.2cm} X}
\toprule
\textbf{Source} & \textbf{Method} & \textbf{Outcome} \\
\midrule
Polymarket Data API
    & REST \texttt{/data/trades}
    & Hard cap of 3{,}100 trades per market.
      The 426 markets exceeding this threshold are the
      highest-volume geopolitical markets — precisely those
      most likely to contain asymmetrically informed wallets.
      Unsuitable as the primary collection method. \\
\addlinespace[4pt]
Dune Analytics
    & SQL query interface
    & Full trade history available in principle, but the
      free tier is capped at $\sim$384{,}000 rows and
      complete access is paywalled. \\
\addlinespace[4pt]
\textbf{Goldsky} \texttt{orderbook-subgraph/0.0.1}
\textbf{(S3 archive)}
    & Compressed snapshot \newline
      \texttt{warproxxx/poly\_data}~\cite{poly_data_github}
    & Full wallet-level history with no row cap,
      spanning 1 Feb 2023 to 7 Oct 2025.
      Selected as the data source for this project
      (see Section~\ref{sec:snapshot_cutoff}). \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Snapshot provenance and cutoff.}
\label{sec:snapshot_cutoff}
The complete \texttt{OrderFilled} event history was obtained from a
community-maintained S3 archive published by
\texttt{warproxxx/poly\_data}~\cite{poly_data_github},
with credit to \texttt{@PendulumFlow} for the original snapshot.
The compressed archive (\texttt{orderFilled\_complete.csv.xz},
5.9\,GB compressed, $\sim$35--40\,GB uncompressed) spans
\textbf{1 February 2023 to 7 October 2025}.
The cutoff is structural: Polymarket migrated to CTF Exchange V2 in
late 2025, introducing a redesigned order struct and account
abstraction support~\cite{polymarket_v2}.
The original Goldsky subgraph (\texttt{orderbook-subgraph/0.0.1}),
which exposed full maker and taker wallet addresses, stopped indexing
at this migration point.
As noted above, the replacement subgraph omits wallet addresses entirely.
The 33-month window captured is nonetheless comprehensive for the
purposes of this project: it covers 1,801 resolved geopolitical
markets, 13\,M trades across 333{,}124 unique wallets, and spans the
full arc of the 2024 US Presidential Election — the single most
active period in Polymarket's history.








% ── 2.2 Pipeline Architecture ─────────────────────────────────────────────────
\subsection{Pipeline Architecture}
\label{sec:pipeline}

The data collection pipeline consists of five Python modules executed
sequentially, with each step's output feeding directly into the next.
The pipeline assumes the raw snapshot has been downloaded first from
the \texttt{warproxxx/poly\_data} S3 archive into \texttt{data/raw/}
(see Appendix~\ref{app:download}).
Figure~\ref{fig:pipeline} shows the full flow from external APIs and
the compressed snapshot through to the analytical DuckDB database.
Full setup and reproduction instructions are provided in the project
README\footnote{\href{https://github.com/johnstew324/polymarket-whale-watch}{%
\faGithub\;\texttt{johnstew324/polymarket-whale-watch}}}.
Listings for the two non-trivial pipeline steps are provided in
Appendix~\ref{app:code}.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance = 0.6cm and 1.5cm,
    api/.style   = {rectangle, rounded corners=3pt,
                    draw=PolyBlue!70, fill=PolyBlue!10,
                    minimum width=3.2cm, minimum height=0.65cm,
                    font=\small\sffamily, align=center},
    script/.style= {rectangle,
                    draw=orange!80, fill=orange!12,
                    minimum width=3.2cm, minimum height=0.65cm,
                    font=\small\ttfamily, align=center},
    file/.style  = {rectangle, rounded corners=1pt,
                    draw=gray!55, fill=gray!8,
                    minimum width=3.2cm, minimum height=0.65cm,
                    font=\small\ttfamily, align=center},
    db/.style    = {cylinder, shape border rotate=90, aspect=0.22,
                    draw=ForestGreen!80, fill=ForestGreen!10,
                    minimum width=3.0cm, minimum height=0.9cm,
                    font=\small\sffamily\bfseries, align=center},
    arr/.style   = {->, >=latex, thick, gray!65},
    labl/.style  = {font=\footnotesize\sffamily\itshape, text=gray!70},
]

% ── Column 1: sources
\node[api]                           (gamma) {Gamma API\\
                                              {\footnotesize /events?tag=geopolitics}};
\node[api, below=1.3cm of gamma]     (clob)  {CLOB API\\
                                              {\footnotesize /markets/\{conditionId\}}};
\node[api, below=1.3cm of clob]      (s3)    {S3 Snapshot\\
                                              {\footnotesize 5.9\,GB compressed}\\
                                              {\footnotesize $\sim$35--40\,GB raw}};

% ── Column 2: scripts
\node[script, right=of gamma]  (cm) {collect\_markets.py};
\node[script, right=of clob]   (ft) {fetch\_tokens.py};
\node[script, right=of s3]     (fx) {filter\_xz.py};

% ── Column 3: intermediate files
\node[file, right=of cm]  (mj) {markets.json\\{\footnotesize 4{,}852 markets}};
\node[file, right=of ft]  (tc) {token\_to\_condition.json\\
                                 {\footnotesize 7{,}998 token IDs}};
\node[file, right=of fx]  (tr) {trades\_raw.csv\\
                                 {\footnotesize 6.49\,M matched rows}};

% ── Column 4: processing (centred between mj and tr)
\node[script,
      right=2.0cm of $(mj)!0.5!(tc)$]
      (pt) {process\_trades.py\\
            {\footnotesize unpivot maker/taker}\\
            {\footnotesize → 13.0\,M wallet rows}};

\node[script, below=0.85cm of pt]  (ld) {load\_db.py};

% ── Column 5: database
\node[db, right=2.2cm of pt]  (ddb) {polymarket.ddb\\(DuckDB)};

% ── Arrows
\draw[arr] (gamma) -- (cm);
\draw[arr] (clob)  -- (ft);
\draw[arr] (s3)    -- (fx);
\draw[arr] (cm) -- (mj);
\draw[arr] (ft) -- (tc);
\draw[arr] (fx) -- (tr);
\draw[arr] (mj.east) -| (pt.north);
\draw[arr] (tc.east) -- (pt.west);
\draw[arr] (tr.east) -| (pt.south);
\draw[arr] (pt.east)  -- (ddb.west);
\draw[arr] (ld.east)  -- ++(0.4,0) |- (ddb.south west);
\draw[arr] (mj.north) -- ++(0,0.35) -| (ld.north);

% ── Column labels
\node[labl, above=0.2cm of gamma] {Sources};
\node[labl, above=0.2cm of cm]    {Collection};
\node[labl, above=0.2cm of mj]    {Intermediate};
\node[labl, above=0.2cm of pt]    {Processing};
\node[labl, above=0.2cm of ddb]   {Database};

\end{tikzpicture}
\caption{Data collection and loading pipeline. Orange: Python scripts
         (\texttt{src/pipeline/}); blue: external data sources; grey:
         intermediate files; green: analytical database.
         Full pipeline reproducible via \texttt{make pipeline}.
         Source: \href{https://github.com/johnstew324/polymarket-whale-watch}{%
         \faGithub\;\texttt{johnstew324/polymarket-whale-watch}}.}
\label{fig:pipeline}
\end{figure}

\begin{table}[H]
\centering
\caption{Pipeline module summary.}
\label{tab:modules}
\small
\begin{tabularx}{\textwidth}{p{4.0cm} p{3.6cm} X}
\toprule
\textbf{Script} & \textbf{Output} & \textbf{Purpose} \\
\midrule
\texttt{collect\_markets.py}
    & \texttt{markets.json}
    & Paginates the Gamma API~\cite{polymarket_docs} across all
      closed geopolitical events.
      Resolved outcome is derived from \texttt{outcomePrices}:
      the token whose price converges to 1 is taken as the winner. \\
\addlinespace[3pt]
\texttt{fetch\_tokens.py}
    & \texttt{token\_to\_condition.json}
    & Retrieves YES/NO ERC-1155 token IDs for every market with
      volume $\geq$\$1{,}000 via the CLOB API.
      Token IDs are the on-chain identifiers present in raw
      \texttt{OrderFilled} events; this mapping is required to
      link blockchain fills to Polymarket condition IDs. \\
\addlinespace[3pt]
\texttt{filter\_xz.py}
    & \texttt{trades\_raw.csv}
    & Stream-filters the compressed snapshot.
      See below. \\
\addlinespace[3pt]
\texttt{process\_trades.py}
    & \texttt{trades\_clean.csv}
    & Unpivots each raw fill into two wallet-centric rows.
      See below. \\
\addlinespace[3pt]
\texttt{load\_db.py}
    & \texttt{polymarket.ddb}
    & Loads cleaned trades and market metadata into DuckDB,
      casting timestamps and converting \texttt{tags} from
      JSON strings to native \texttt{VARCHAR[]} arrays.
      See Section~\ref{sec:schema}. \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{\texttt{filter\_xz.py} — streaming the compressed snapshot.}
Decompressing the full 5.9\,GB archive to disk was not feasible during
development: at $\sim$35--40\,GB uncompressed the file exceeded
available local storage.
\texttt{filter\_xz.py} avoids this by piping \texttt{xzcat} into a
Python CSV reader, processing the 150\,M-row snapshot as a stream
without ever materialising the full file.
Each row is checked against the token map produced by
\texttt{fetch\_tokens.py}: if either the \texttt{makerAssetId} or
\texttt{takerAssetId} matches a known outcome token, the row is written
to \texttt{trades\_raw.csv} with the resolved \texttt{condition\_id}
appended.
The filter reduces 150\,M rows to 6.49\,M matched rows — roughly 4\%
of the snapshot — in a single streaming pass
(Appendix~\ref{app:code}, Listing~\ref{lst:filter_xz}).
A cross-platform fallback using Python's \texttt{lzma} module is
included in the script for Windows environments where \texttt{xzcat}
is unavailable.

\paragraph{\texttt{process\_trades.py} — unpivoting to wallet-centric rows.}
Raw \texttt{OrderFilled} events record each fill as a single row
containing both the maker and taker wallet.
Querying by wallet directly would otherwise require scanning both
columns on every lookup.
\texttt{process\_trades.py} unpivots each raw fill into two
wallet-centric rows — one for the maker and one for the taker —
each with an explicit \texttt{side} (BUY or SELL), normalised USD and
token amounts (raw on-chain values divided by $10^6$ for USDC's
6-decimal precision), and a derived \texttt{price} computed as
$\texttt{usd\_amount} / \texttt{token\_amount}$.
This doubles the row count from 6.49\,M fills to 13.0\,M wallet
records and is what enables the wallet-level aggregations used
throughout the analysis.
Dust trades where the normalised token amount rounds to zero are
discarded (Appendix~\ref{app:code}, Listing~\ref{lst:process_trades}).